Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-07 paper.qmd
Changed the sequqntial color palatte for Five_Gau clusters example

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 76
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

error_df_gau_umap <- error_df_gau_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(0.47, 0.5475)) + ylim(c(0.0125, 0.09)) +
  scale_colour_continuous_sequential(palette = "Blues") +
  interior_annotation("b3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 33
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

error_df_gau_pacmap <- error_df_gau_abs |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(-0.02, 0.18)) + ylim(c(0.12, 0.32)) +
  scale_colour_continuous_sequential(palette = "Blues") +
  interior_annotation("c3", 
                      position = c(0.08, 0.9),
                      cex = 2)

>>>>

## Compute hexbin parameters
num_bins_x_gau1 <- 13
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

## Compute hexbin parameters
num_bins_x_gau1 <- 45
lim1 <- gau1_scaled_obj$lim1
lim2 <- gau1_scaled_obj$lim2
r2_gau1 <- diff(lim2)/diff(lim1)

@@

error_df_gau_umap <- error_df_gau_abs |>
  ggplot(aes(x = UMAP1,
             y = UMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(0.47, 0.5475)) + ylim(c(0.0125, 0.09)) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  interior_annotation("b3", 
                      position = c(0.08, 0.9),
                      cex = 2)

@@

@@

error_df_gau_pacmap <- error_df_gau_abs |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.5) + 
  xlim(c(-0.02, 0.18)) + ylim(c(0.12, 0.32)) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  interior_annotation("c3", 
                      position = c(0.08, 0.9),
                      cex = 2)
